\section{Motivation}
This project revolves around the use of augmented reality (AR) navigation on smartphones. AR is the superimposing of a computer-generated image onto a user's view of the real world \cite{oxforddict}. This technology first came about in the 1960s \cite{InteractionDesign} but recently gained wide-spread consumer attention after the use of it on Snapchat filters \cite{Snapchat}, and the 2016 game \textit{Pokémon Go}. 

The need for such an \annote{application}{what is our application?} is justifiable. People find themselves lost in unfamiliar spaces such as museums, immersed by the culture around them. This project aims to tackle this issue by allowing users to restore their orientation by having an AR platform, routing users to their destination. This approach is considerably more extensive, and dynamic in comparison to the existing 2-D solutions available in the market. The platform will use the device's camera to work out its surrounding, and produce a highlighted line on the screen to their destination in real-time.

This concept has various applications to other scenarios such as finding products in a supermarket, or books in a library. Furthermore, the concept could also use machine learning in identifying user traits in places visited in a museum in order to give personalised recommendations at other similar exhibitions.

\section{Purpose \& Scope}
% complete
The purpose of the project is to provide a solution to the problem at hand. A real-time navigation system to assist users to their desired location within a museum. The significant part of this project is achieved by calculating the quickest route to the user's destination based from the user's current location, and displaying this route on the user's device through the implementation of AR-assisted superimposition of navigational lines that the user would follow.

\section{Assumptions}
% complete
It is assumed that the reader is familiar with the supporting documents of this report, including the proposal, system requirements specification, the documentation, testing and deployment plans. These documents outline the concept of the project and detail the procedures to achieve the purpose of the project.

\section{Coverage}
% complete - can cut down words here
This report fully describes the project undertaken, containing eight main sections:

\begin{enumerate}
	\item Introduction - Gives an introduction to the project, outlining the motivation, purpose and scope of the project. \remove{It also} Includes any assumptions based on the reader regarding any prior reading and the coverage of this report.
	\item Background - Analysis of current projects and literature available in this area. It also contains analysis of AR libraries which held potential to be implemented, and a discussion of the technologies behind each of the proposed libraries as well as their respective Operating System (OS). Further, an analysis on the use of Arduino and Rasberry Pis in current solutions.
	\item Project Management - Providing a breakdown of the development methodology and justification of adopted approaches. This section of the report will also analyse the Software Development Life Cycle (SDLC) and outline the roles of all members involved.
	\item Requirements - Outlining the various requirements of the project; the gathering of user requirements to be able to develop a minimal viable product for end-users. Analysing the stakeholder, system, functional and non-functional requirements.
	\item Design - This section will define how the system will achieve its purpose. Analysing the different use cases and activities of the application. Discussing the technical architecture, user interface and accessibility features of the application whilst ackowledging at which parts of process user consultation was necessary.
	\item Implementation - Discussion of the implementation and justification of the decisions made. Detailed reports with reference to the backlog of the development, outlining sprints, splitting up front-end \& back-end development and system hardware. Included in this section is also reports of how the team enforced ethical audit, evaluation of the challenges that were faced during implementation and what steps were taken to overcome these challenges.
	\item Testing \& Quality Assurance - Analysis of the test-driven development approach adopted by the team and discussion of the various types of testing conducted:
		\begin{itemize}
			\item Unit Testing
			\item Integration Testing
			\item Performance and Stress Testing
			\item Regression Testing
			\item User Acceptance Testing
			\item Beta Testing
		\end{itemize}
	In addition, a formative evaluation will be given in subject of testing and detailed reviews of the function and non-functional requirements in regards to the original purpose of the project.
	\item Project Evaluation - Evaluation of the success of the implementation in meeting the needs discovered in the background research is given in quantitative and qualitative terms. Analysis of the successes and failures of the project, and discussion of the advances made. Possible extensions and further work that could be undertaken are then discussed.
\end{enumerate}

In addition to these main sections there is a glossary and bibliography of references at the end of the report, along with a number of appendices. These appendices contain:

\begin{itemize}
	\item Appendix A - Research conducted around end-users and stakeholders which were key in requirements gathering.
	\item Appendix B - User stories and scenarios in which a user would use the application. Screenshots of the user interface and camera activity and the procedure in which the user would use the application are given.
	\item Appendix C - The System Requirements Specification: includes the purpose, scope, system overview, references, definitions, use cases, functional and non-functional requirements.
	\item Appendix D - The Documentation Plan: outlines the strategy for creating all documentation associated with the sofware release.
	\item Appendix E - The Testing Plan: in accordance to the IEEE Standard for Software Test Documentation (ANSI/IEEE Standard 829-1983), outlines and describes the testing approach and overall framework that was followed during the implementation phase.
	\item Appendix F - The Deployment Plan: designed to ensure that the system successfully reaches its users and maintenance of the system allows for new features to be delivered seamlessly. Details further information about the development of the system.
	\item Appendix G - The testing conducted during the implementation and development phase of the project.
	\item Appendix H - User \& Stakeholder feedback.
\end{itemize}