% You should identify the stakeholders of any software you are developing and reason that they have an interest in your concept.

The main stakeholders are museum visitors and staff. After consulting with them, and potential users of the proposed application, we were able to gain a better understanding of what the apparent need was in the relative market regarding museums. Out of the 21 responses received, 15 potential users admitted to visiting museums at least once a month. This shows some level of frequency in their visits, and that there is something that can be offered to this group of people.\\

Since our concept principally considers the use of navigation in museums, when users were asked, "do you find yourself using the maps in the museum more than once?"- a very reassuring 100\% of visitors had agreed that they did in fact refer to the maps around the museum more than once, some respondents going on to say that they referred to it over 10 times. However, these maps are not free; in most museums, including the Natural History Museum and the Science Museum in London, require a fee of £1.\\

18 of the respondents had agreed they would much rather prefer using their phone to navigate rather than the paper maps. This shows that there is an evident need for an accessible tool other than the maps around the museum in order to assist visitors' navigation around the museum.\\

Based on the stakeholder research, the project requirements are, 

\begin{itemize}
    \item navigate the user to a museum through the use of augmented reality
    \item to display navigational routes in real time
    \item calculate the shortest route to the user specified location 
    \item work transferrably in other museums/commercial spaces
    \item contain accessibility features such as magnified text and inverted colours for example
\end{itemize}

One key stakeholder whom would be affected are the museum staff as they would be instrumental to any on-the-ground assistance and would be the first point of contact for assistance in navigation. Furthermore, the platform should endeavour to make the jobs undertaken by museum staff with relation to the parameters of platform easier.\\

The stakeholder requirements of museum staff are,

\begin{itemize}
    \item Exhibit an effective and easy-to-use design. 
    \item Be economic and effective in its use of data, as most data the app would download would be sourced from in-museum Wi-Fi. 
    \item Written content and other media to be within control of the museum.
\end{itemize}

During our field research we spoke to museum-floor staff and receptionists. Most importantly, all staff members whom we spoke to had received a navigational inquiry, either from themselves or members of public. All staff responded positively to the use of a phone but cited concerns about efficiency of the concept with specific references to battery performance and data usage. One major concern highlighted by every member of museum staff was ease of use, and therefore, we suggested to supply a solution to this by designing a simple and efficient graphical user interface. Another potential factor that became apparent upon speaking to staff was the fetching of information and data - aiming to minimalise the use of data where necessary.