% The essential functional elements should be defined and described, including data paths. This functional specification should not assume any specific technologies, only functional technologies (e.g. short range wireless technology is a functional statement whilst Bluetooth is a specific technology)

The main functional elements of the concept are:

\begin{enumerate}
\subsection*{Route Calculations}
    \item Receiving the \textbf{current coordinates} of the user, and the coordinates of the destination will be needed to create the starting and end points for calculating the route. The current location will come from sensors on the user's device, and the destination location will be queried against a mapping system.
    \item The platform can \textbf{calculate the quickest route between two points} specified by the user. Data from the above, and the museum model will be required for this calculation.

\subsection*{Superimposition}
    \item A \textbf{3D line will be superimposed} that navigates the user to their destination. Sensor data from the user's device along with the user's relative position in the model will be required to show the line. Access to the user's camera is essential in this element.

\subsection*{Suggestions/Reviewal}
    \item When the user arrives at their destination, the \textbf{system will give recommendations} based on their current route, allowing them to rate their journey.
    \item The \textbf{user's camera can recognise artwork/objects}, displaying further information about the piece. A storage area of current pieces in the museum will exist so that the camera can query the information.
\end{enumerate}
